\begin{titlepage}
\title{2018 SpeedStudy \thanks{An adventure to explore how much of MITOCW's 
(Computer Science, Physics and Mathematics) Curriculum I can thoroughly learn in a year.}}
\author{P1xt }
\maketitle
\section{Abstract}

I'm tackling my 2018 learning goals in true "Speedrun" style. The following list contains far more than I expect I'll be able to complete in 2018, so it's sufficient that I can speedrun the year without running out of items from the list to learn.

My dual main goals are to A) study algorithms in depth and B) explore Physics. To that end, I am including a variety of Computer Science, Mathematics and Physics courses, with no prescribed order. I'll just select the next course in whatever list I'm most inspired to continue each time I'm ready to progress to a new course.

Additionally, I'm including a variety of "bonus point" opportunities for reading books, completing projects, and completing algorithmic challenges.

My goal is to see how many points I can rack up by December 31, 2018.

\textbf{Current Course:} 18.01\\
\textbf{Total Points:} 0

\begin{dndtable}
    \textbf{Activity}  & \textbf{Points} \\
Basic Project & 100 \\
Substantial Project & 200 \\
Large Project & 300 \\
Gigantic Project & 400 \\
Duolingo (1 level) & 100 \\
Book & 200 \\
Tutorial site (Udemy/Pluralsight/Egghead/Treehouse/etc) course & 100  \\
University level course (Coursera/edX/MITOCW/etc)  & 500 \\
Physical Activity (30 minutes) & 10 \\
Analytics Vidhya Competition & 50  \\
Crowd Analytix Competition & 50  \\
Kaggle Competition & 50  \\
Driven Data Competition & 50 \\
Blog Post on any topic & 15  \\
Blog Post Tutorial & 40 \\
Video Tutorial & 50  \\
Open Source PR & 50  \\
Module to npm & 200  \\
Team Up for a project & 100  \\
CodeWars (10 problems) & 50  \\
CodinGame (1 Tier) & 100  \\
CodinGame (1 Bot Competition) & 20  \\
HackerRank (10 problems) & 50  \\
Google Code Jam (1 round from past contest) & 100 
\end{dndtable}
\end{titlepage}